### 2016-05-13 Paper/Paper.tex
paper in discussion

\section{Discussion and Analysis}
\subsubsection{Fuzzy c-Means Results}\label{fcmr}

We stopped at k = 10 because FPC became 1

@@

>>>>

\section{Discussion and Analysis}
\subsubsection{Fuzzy Clustering Results}\label{fcmr}
Before we discuss the resulting model's implications for analysis of potential carbon storage sites, we must select one of the model's presented in Figure \ref{clusterfig} as the best model. 
The partition coefficient (FPC) will be important in choosing our preferred model. In discussing the partition coefficient following in the work of \cite{dunnbar} writing $FPC = \frac{1}{N}\sum_{k = 1}^k \sum_{i = 1}^N m_{ik}^2$. From this definition of the partitioning coefficient we find that $FPC = \frac{1}{k}$, when a given vector $j$ belongs equally to all $k$ clusters and that $FPC = 1$ when $j_{k_i} = 1$ for a unique value of $i$ and $j_{k_i} = 0$ for all other values of $i$, such that $i \in [1, k]$. Now given $FPC \in [\frac{1}{k}, 1]$ we set an optimal value of $FPC_k = avg(\frac{1}{k}, 1) =  \frac{1+k}{2k}$. 
Originally, the clustering algorithm was to be run $\forall k \in [5,11]$. As per Figure \ref{clusterfig}, this was resolved to a maximum value of $k = 10$ because at $k = 10$ we see $FPC_10 = 1$. In examining $k = 9$, we find that $FPC_9 = \frac{10}{18} \approx \frac{11}{18}$, the optimal value of $FPC$ for $k = 9$. For all $k$, this is the closest value of $FPC_k$ to the optimal value of $FPC_k$, which immediately makes the clustering analysis for $k = 9$ the favorable choice.

@@

\bibitem{dunnbar}
Trauwaert, E. 
\textit{On the meaning of Dunn's partition coefficient for fuzzy clusters}
Fuzzy sets and systems 25.2 (1988): 217-242.
